Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-17 paper/intro.tex
work on the acronum paragraph so that it typesets better

BriefCASE provides access to two analysis tools (GearCASE~\cite{gearcase2020} and DCRYPPS~\cite{dcrypps2019}) that can examine AADL models for potential cyber vulnerabilities and suggest cyber-security requirements to mitigate them.
A library of architectural transforms guides systems engineers through automated model transformations that modify the architecture to address these requirements, possibly inserting new high-assurance components into the system. 
Implementations for these new high-assurance components are synthesized from formal specifications using the Semantic Properties for Language and Automata Theory (SPLAT) tool~\cite{slind-hcss2020},~\cite{formal-filter-synth-langsec}.
Formal verification that the transformed system model satisfies its cyber requirements is accomplished via the Assume Guarantee Reasoning Environment (AGREE)~\cite{agree2013}.
%The AGREE analysis \emph{assumes} properties on the inputs of a given component of the system, and attempts to formally prove the conjectured \emph{guarantees} of the output. 
AGREE is a {\em compositional assume-guarantee} style model checker for AADL models that attempts to prove properties about one layer of the architecture using
properties allocated to its subcomponents.
Cyber-resilient code implementing the verified model is then automatically generated using the High Assurance Modeling and Rapid Engineering for Embedded Systems (HAMR) toolkit~\cite{hamr}.  If desired, this code can be targeted to the formally verified seL4 secure microkernel~\cite{sel4-2009}.

>>>>

BriefCASE incorporates model-level cyber-analysis tools (presently
GearCASE~\cite{gearcase2020} and DCRYPPS~\cite{dcrypps2019}) which can
examine AADL models for potential vulnerabilities and suggest
cyber-security requirements to mitigate them.  A library of
architectural transforms guides the system engineer through automated
model transformations that modify the architecture to address these
requirements, possibly inserting new high-assurance components into
the system.  Implementations for the new components are synthesized
from formal specifications using
SPLAT~\cite{slind-hcss2020},~\cite{formal-filter-synth-langsec}
(Semantic Properties for Language and Automata Theory).  Formal
verification that the transformed system model meets its requirements
is accomplished via AGREE~\cite{agree2013} (Assume Guarantee Reasoning
Environment).
%The AGREE analysis \emph{assumes} properties on the inputs of a given component of the system, and attempts to formally prove the conjectured \emph{guarantees} of the output.
AGREE is a {\em compositional assume-guarantee} style model checker
for AADL models that attempts to prove properties about one layer of
an architecture using properties allocated to its subcomponents.
Cyber-resilient code implementing the verified model is then
automatically generated using the High Assurance Modeling and Rapid
Engineering for Embedded Systems (HAMR) toolkit~\cite{hamr}.  If
desired, this code can be targeted to the formally verified seL4
secure microkernel~\cite{sel4-2009}.
